Global Deaths Due to Air Pollution

### 2022-05-02 outline.Rmd
Added title and lable to boxplot

ggplot(high_pop_countries, aes(x=Country.Name, y=Count))+
  geom_boxplot()

@@

ggplot(low_pop_countries, aes(x=Country.Name, y=Count))+
  geom_boxplot()

>>>>

ggplot(high_pop_countries, aes(x=Country.Name, y=Count, color=Country.Name))+
  geom_boxplot()+
  labs(title="Selection of high-population countries", x="Country", y="Population (in millions)")

@@

ggplot(low_pop_countries, aes(x=Country.Name, y=Count, color=Country.Name))+
  geom_boxplot()+
  labs(title="Selection of low-population countries", x="Country", y="Population (in millions)")
